### 2019-04-24 README.Rmd

### rob_summary_tools()
Outputs a list of the risk of bias assessment tools for which a template currently exists in rob_suumary(). Users can currently produce summary plots for three commonly used tools: ROB2.0, ROBINS-I and QUADAS-2. We expect this list to be updated in the near future to inlcude tools such as ROBIS (tool for assessing risk of bias in systematic reviews).

@@

This project is licensed under the MIT License - see the [LICENSE.md](LICENSE.md) file for details

@@

* Emily Kothe for contribution to `ggplot2` coding issues

>>>>

### rob_summary_tools()
Outputs a list of the risk of bias assessment tools for which a template currently exists in rob_summary(). Users can currently produce summary plots for three commonly used tools: ROB2.0, ROBINS-I and QUADAS-2. We expect this list to be updated in the near future to inlcude tools such as ROBIS (tool for assessing risk of bias in systematic reviews).

@@

This project is licensed under the MIT License - see the [LICENSE.md](https://github.com/mcguinlu/robvis/blob/traffic_light_plot/LICENSE) file for details.

@@

* [Emily Kothe](https://github.com/ekothe) for help in fixing `ggplot2` coding issues.
* [Eliza Grames](https://github.com/elizagrames) for creating the `robvis` hex sticker.
